---
title: "Cabbages"
author: "Eden Williams"
date: "Summer 2022"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  
$H_O$: There is no difference in average Vitc between c39 and c52 cultivation methods.   
$H_A$: There is a difference in the cultivation methods of average Vitc between c39 and c52.  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
We are explaining the numerical variable of vitamin C content by evaluating the categorical variable of cultivation. We are using a t-test to compare the vitamin C content between the two groups.
  
# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

```{r}
boxplot(VitC~Cult,data=veggy)
```

Here we have a graph showing the different cultivation methods and the difference in the amount of Vitamin C they produce. While we can see the c52 is producing a larger amount of Vitamin C it does not necessarily mean that it is the most effecient method. We will not know until we perform a t-test.  


<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(VitC~Cult,data=veggy)
```

In this graph we can see that the average amount of Vitamin C produced by cultivation method c52 is 64.4. The average amount of Vitamin C produced by cultivation method c39 is is 51.5. Based on this data it seems that cultivation method c52 is more reliable in producing higher amounts of Vitamin C.  


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```

The p-value is 0.00000003405. The chances of a differing result are nearly impossible based on the p-value. This means that we can reject the null hypothesis since the probability is so small.   


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Based on the following information that we collected, it is safe to say that we can reject the null hypothesis, which states that the amount of Vitamin C produced is not affected by the cultivation method. Based on our data we can see that the cultivation method does in fact affect the amount of Vitamin C that will be produced. 
